
\chapter{Background Theory}

\label{ch:background}

\section{Introduction}

Wi-fi routers provide a signal that degrades with distance. Signal boosters are therefore normally required to increase signal strength, in essence 'repeating' the signal.
University Hall has three signal repeaters that are meant to serve the entire hall of residence.

\section{Summary of Findings}
Participants in the survey were asked three simple questions.
\begin{itemize}
    \item What device do you use to access the network?
    \item On a scale of zero to five, what is the quality of the network that you can access from your room?
    \item On a scale of zero to five, what is the quality of the network that you can access from outside your block?
    \item On a scale of zero to five, what is the best quality of the network you have ever experienced on MakAir from within the hall? Where was this?
\end{itemize}

I present the averages gathered from each block. A total of three participants were interviewed from each block.

\begin{table}
    \centering
    \begin{tabular}{|c|c|c|c|c|}
        Block & Room? & Outside? & Best location? & Where? \\
        B & 2 & 3 & 3.5 & Right Booster \\
        C & 0 & 1 & 3.5 & Right Booster \\ 
        D & 0 & 1 & 3 & Right Booster \\
        F & 2 & 2 & 2 & Right Booster \\
        G & 2 & 3 & 4 & Left Booster \\
        H & 0.5 & 1 & 2.5 & Central Booster \\
        L & 0 & 1 & 2.5 & Left Booster \\
        M & 0 & 2 & 4 & Left Booster \\
        N & 3 & 4 & 4 & Left Booster \\
        P & 0 & 4 & 4 & Left Booster \\
        R & 0 & 3 & 4 & Left Booster \\
        S & 1 & 3 & 4 & Left Booster \\
    \end{tabular}
    \caption{Summary of statistics from interview findings}
    \label{tab:my_label}
\end{table}

There were a few strong observations from this data.
\begin{itemize}
    \item Individuals whose windows faced outside the hall had next no network signal or none at all.
    \item Individuals accessing the network with mobile phones generally hard a weaker signal than those with personal computers
    \item Individuals whose rooms were located behind a booster had a poor signal strength
    \item The strongest signals were reported while standing right in front of the left, center or right boosters
    \item The signal strength starts to degrade at 15m from the booster
\end{itemize}